Elders health and elder files data cleaning

### 2020-04-13 elders_health_data_cleaning.Rmd
udpate file path method/backup

```{r}
# Load data
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
```

>>>>

```{r}
input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/Input/")
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/Output/")
input_file <- c("elders_ids_linked.rds")
output_file <- c("elders_ids_linked.rds")

# Load data
elders_ids_linked <- read_rds(paste0(output_path, input_file))
```
